Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-12 hscc2017/paper.tex
hscc17

%------------------------------------
\subsection{Verifying Closed-loop Control Systems \\ \blue{Under the Effect of Imprecisions, Quantization, and Finite Word Length Representation}}
\label{verifying-closed-loop-control-systems}
%------------------------------------

@@

The parametric uncertainties in the plant are assumed to have the same
order as the plant model, since tolerances of higher order would invalidate
feedback model (even tiny errors of higher order can move the poles by a
large amount preventing any single controller from stabilizing such a setup).
This is a reasonable assumption since most tolerances do not change the 
architecture of the plant, and models subject to such effects are
inadequate.

>>>>

%------------------------------------
\subsection{Verifying Closed-loop Control Systems \\ \blue{Model Imprecision, Quantization Effects, and Finite Word Length Representation}}
\label{verifying-closed-loop-control-systems}
%------------------------------------

@@

The parametric uncertainties in the plant are assumed to have the same
order as the plant model, since 
%tolerances of higher order would invalidate the feedback model (even tiny 
errors of higher order can move the closed-loop poles by large amounts, 
thus preventing any given controller from stabilizing such a setup. 
This is a reasonable assumption since most tolerances do not change the 
architecture of the plant. 
%, and models subject to such effects are inadequate.
